Real-time Thrust Estimation and Regulation for Multirotor Aerial Vehicle\\ {} \thanks{}

### 2018-09-16 paper/drafts/IEEE_VERSION.tex
Now were actually done

There has been an enormous strive to develop methods to obtain a closed loop control system for UAVs. The methods range from thrust modeling to estimation using different sensors. The majority of the estimation-based controls rely on the voltage or current drawn by the motors.
Awan et. al. \cite{awan} developed an adaptive observer-based thrust estimation system. This method allowed the MAV to maintain a hover with higher precision compared to previous methods involving thrust estimation. However, their proposed structure only accounts for hovering condition and the models were based around a linearized system. As a result, the system was highly violable for disturbances. This was accounted in Sydney et. al. \cite{sydney}, where they have proposed a highly complex estimation system and considered the nonlinear model of the system. Similarly, Mahoney et. al. \cite{mahoney1} devised a system which estimates the thrust using an iterative based calculation. This system while it allows for a valid estimation of the thrust, it is relatively complex and requires heavy computation. Letter in Mahony (2017), they have improved the estimation algorithm using the feedback signal of the voltage and current given to the motor by the ESC. Their system works to maintain a thrust given some disturbance. Still, their system runs through an iterative loop before detecting an appropriate response to extraneous forces. This system while it allows for a robust estimation of the thrust, it is still a complex system. As well their method requires a significant amount of calibration for both the propellers and rotors which makes it harder to employ in different systems. Streit \cite{streit} developed a control system to compensate for wind disturbances using a pitot-tube sensor along with an accompanying estimation algorithm. While this seems similar to the Yeo et al paper, there are some major differences. Streit \cite{streit} has only one pitot sensor onboard the UAV which is unidirectional and therefore only applies to forward motion. As well the pitot-tube is made of brass and therefore not feasible for all smaller UAV’s as it will be too heavy. Yeo et al have used fabricated pitot tubes placed below each propeller to measure the rotor downwash and compare them to the estimated expected wind speed. Their system is ultimately used to localize external noise from other UAV’s and therefore an exceedingly accurate measurement is not as important. While the sensor can accurately measure wind speed accurately during vertical motion, there is a significant divergence from the ground speed measurement during lateral movement. As well there is a very limited range of speeds that are available for measurement from the probe. There are some works which have used strain guages and hall effect sensors or even torque measurements to obtain the thrust

@@

\begin{thebibliography}{00}
\bibitem{bara}B. J. Emran, D. D. Tannant, and H. Najjaran, “Low-altitude aerial methane concentration mapping,” Remote Sens., vol. 9, no. 8, 2017.
\bibitem{Mathe} K. Máthé and L. Buşoniu, “Vision and Control for UAVs: A Survey of General Methods andof Inexpensive Platforms for Infrastructure Inspection,” Sensors, vol. 15, no. 7, pp. 14887–14916, 2015.
\bibitem{akf} A.H.Mohamed and K. P. Schwarz, “Adaptive Kalman Filtering for INS/GPS,” J. Geod., vol. 73, no. 4, pp. 193–203, 1999.
\bibitem{fuzzy} P. J. Escamilla-Ambrosio and N. Mort, “Development of a fuzzy logic-based adaptive Kalman filter,” in Control Conference (ECC), 2001 European, 2001, pp. 1768–1773.
\bibitem{sebesta} K. D. Sebesta and N. Boizot, “A real-time adaptive high-gain EKF, applied to a quadcopter inertial navigation system,” IEEE Trans. Ind. Electron., vol. 61, no. 1, pp. 495–503, 2014.
\bibitem{Manki} A. Makni, H. Fourati, and A. Y. Kibangou, “Energy-Aware Adaptive Attitude Estimation under External Acceleration for Pedestrian Navigation,” IEEE/ASME Trans. Mechatronics, vol. 21, no. 3, pp. 1366–1375, 2016.
\bibitem{Lin} C. M. Lin and C. S. Hsueh, “Adaptive EKF-CMAC-based multisensor data fusion for maneuvering target,” IEEE Trans. Instrum. Meas., vol. 62, no. 7, pp. 2058–2066, 2013.
\bibitem{Sharman} M. K. Al-Sharman, M. A. Jaradat, and M. F. Abdel-Hafez, “Intelligent attitude and flapping angles estimation of flybarless helicopters under near-hover conditions,” J. Franklin Inst., 2018.
\bibitem{Emran} M. K. Al-Sharman, B. J. Emran, M. A. Jaradat, H. Najjaran, R. Al-Husari, and Y. Zweiri, “Precision landing using an adaptive fuzzy multi-sensor data fusion architecture,” Appl. Soft Comput. J., vol. 69, 2018.
		\bibitem{mahoney1} Mahoney 2012
\bibitem{rcb} https://www.rcbenchmark.com/dynamometer-series-1580/
\bibitem{md} https://moderndevice.com/product/wind-sensor-rev-p/
\bibitem{hot_wire} Extended Applications of the Hot‐Wire Anemometer, Stanley Corrsin,Review of Scientific Instruments 1947 18:7, 469-471 
\bibitem{awan} A. U. Awan, J. Park and H. J. Kim, "Thrust estimation of quadrotor UAV using adaptive observer," 2011 11th International Conference on Control, Automation and Systems, Gyeonggi-do, 2011, pp. 131-136.
\bibitem{sydney} N. Sydney, B. Smyth and D. A. Paley, "Dynamic control of autonomous quadrotor flight in an estimated wind field," 52nd IEEE Conference on Decision and Control, Florence, 2013, pp. 3609-3616.
\bibitem{streit} B. Arain and F. Kendoul, "Real-time wind speed estimation and compensation for improved flight," in IEEE Transactions on Aerospace and Electronic Systems, vol. 50, no. 2, pp. 1599-1606, April 2014.
\bibitem{yeo}Derrick Yeo, University of Maryland, College Park; Nitin Sydney, University of Maryland, College Park; Derek A. Paley, University of Maryland, College Park; Donald Sofge, Naval Research Laboratory AIAA Guidance, Navigation, and Control Conference Kissimmee, Florida

\end{thebibliography}
\end{document}

>>>>

There has been an enormous strive to develop methods to obtain a closed loop control system for UAVs. The methods range from thrust modeling to estimation using different sensors. The majority of the estimation-based controls rely on the voltage or current drawn by the motors.
Awan et. al. \cite{awan} developed an adaptive observer-based thrust estimation system. This method allowed the MAV to maintain a hover with higher precision compared to previous methods involving thrust estimation. However, their proposed structure only accounts for hovering condition and the models were based around a linearized system. As a result, the system was highly violable for disturbances. This was accounted in Sydney et. al. \cite{sydney}, where they have proposed a highly complex estimation system and considered the nonlinear model of the system. Similarly, Mahoney et. al. \cite{mahoney1} devised a system which estimates the thrust using an iterative based calculation. This system while it allows for a valid estimation of the thrust, it is relatively complex and requires heavy computation. Letter in Mahony (2017), they have improved the estimation algorithm using the feedback signal of the voltage and current given to the motor by the ESC. Their system works to maintain a thrust given some disturbance. Still, their system runs through an iterative loop before detecting an appropriate response to extraneous forces. This system while it allows for a robust estimation of the thrust, it is still a complex system. As well their method requires a significant amount of calibration for both the propellers and rotors which makes it harder to employ in different systems. Streit \cite{streit} developed a control system to compensate for wind disturbances using a pitot-tube sensor along with an accompanying estimation algorithm. While this seems similar to the Yeo et al paper, there are some major differences. Streit \cite{streit} has only one pitot sensor onboard the UAV which is unidirectional and therefore only applies to forward motion. As well the pitot-tube is made of brass and therefore not feasible for all smaller UAV’s as it will be too heavy. Yeo et al have used fabricated pitot tubes placed below each propeller to measure the rotor downwash and compare them to the estimated expected wind speed. Their system is ultimately used to localize external noise from other UAV’s and therefore an exceedingly accurate measurement is not as important. While the sensor can accurately measure wind speed accurately during vertical motion, there is a significant divergence from the ground speed measurement during lateral movement. As well there is a very limited range of speeds that are available for measurement from the probe. There are some works which have used strain guages and hall effect sensors or even torque measurements to obtain the thrust value through similar mathematical relationships. The last method that is availble in research is a variable pitch propeller through the research of Cutler. et. al \cite{cutler}. This again is mathematically sound, but in practice has far too many moving parts and is most likely to fail due to mechanical issues

@@

\begin{thebibliography}{00}
\bibitem{bara}B. J. Emran, D. D. Tannant, and H. Najjaran, “Low-altitude aerial methane concentration mapping,” Remote Sens., vol. 9, no. 8, 2017.
\bibitem{Mathe} K. Máthé and L. Buşoniu, “Vision and Control for UAVs: A Survey of General Methods andof Inexpensive Platforms for Infrastructure Inspection,” Sensors, vol. 15, no. 7, pp. 14887–14916, 2015.
\bibitem{akf} A.H.Mohamed and K. P. Schwarz, “Adaptive Kalman Filtering for INS/GPS,” J. Geod., vol. 73, no. 4, pp. 193–203, 1999.
\bibitem{fuzzy} P. J. Escamilla-Ambrosio and N. Mort, “Development of a fuzzy logic-based adaptive Kalman filter,” in Control Conference (ECC), 2001 European, 2001, pp. 1768–1773.
\bibitem{sebesta} K. D. Sebesta and N. Boizot, “A real-time adaptive high-gain EKF, applied to a quadcopter inertial navigation system,” IEEE Trans. Ind. Electron., vol. 61, no. 1, pp. 495–503, 2014.
\bibitem{Manki} A. Makni, H. Fourati, and A. Y. Kibangou, “Energy-Aware Adaptive Attitude Estimation under External Acceleration for Pedestrian Navigation,” IEEE/ASME Trans. Mechatronics, vol. 21, no. 3, pp. 1366–1375, 2016.
\bibitem{Lin} C. M. Lin and C. S. Hsueh, “Adaptive EKF-CMAC-based multisensor data fusion for maneuvering target,” IEEE Trans. Instrum. Meas., vol. 62, no. 7, pp. 2058–2066, 2013.
\bibitem{Sharman} M. K. Al-Sharman, M. A. Jaradat, and M. F. Abdel-Hafez, “Intelligent attitude and flapping angles estimation of flybarless helicopters under near-hover conditions,” J. Franklin Inst., 2018.
\bibitem{Emran} M. K. Al-Sharman, B. J. Emran, M. A. Jaradat, H. Najjaran, R. Al-Husari, and Y. Zweiri, “Precision landing using an adaptive fuzzy multi-sensor data fusion architecture,” Appl. Soft Comput. J., vol. 69, 2018.
		\bibitem{mahoney1} Mahoney 2012
\bibitem{rcb} https://www.rcbenchmark.com/dynamometer-series-1580/
\bibitem{md} https://moderndevice.com/product/wind-sensor-rev-p/
\bibitem{hot_wire} Extended Applications of the Hot‐Wire Anemometer, Stanley Corrsin,Review of Scientific Instruments 1947 18:7, 469-471 
\bibitem{awan} A. U. Awan, J. Park and H. J. Kim, "Thrust estimation of quadrotor UAV using adaptive observer," 2011 11th International Conference on Control, Automation and Systems, Gyeonggi-do, 2011, pp. 131-136.
\bibitem{sydney} N. Sydney, B. Smyth and D. A. Paley, "Dynamic control of autonomous quadrotor flight in an estimated wind field," 52nd IEEE Conference on Decision and Control, Florence, 2013, pp. 3609-3616.
\bibitem{streit} B. Arain and F. Kendoul, "Real-time wind speed estimation and compensation for improved flight," in IEEE Transactions on Aerospace and Electronic Systems, vol. 50, no. 2, pp. 1599-1606, April 2014.
\bibitem{yeo}Derrick Yeo, University of Maryland, College Park; Nitin Sydney, University of Maryland, College Park; Derek A. Paley, University of Maryland, College Park; Donald Sofge, Naval Research Laboratory AIAA Guidance, Navigation, and Control Conference Kissimmee, Florida
\bibitem{cutler}  M. Cutler, J. P. How, "Analysis and Control of a Variable-Pitch Quadrotor for Agile Flight," 2015
J. Dyn. Sys., Meas., Control 137(10), 101002
\end{thebibliography}
\end{document}
